Runtime Feedback in a Meta-Tracing JIT for Efficient Dynamic Languages

### 2011-03-30 talk/icooolps2011/paper.tex
minor language rephrasing

For space reasons we cannot perform a full evaluation here, but still want to
present some benchmark numbers. We chose to present two benchmarks, a port of
the classical Richards benchmark in Python and a Python version of the Telco
decimal benchmark\footnote{\texttt{http://speleotrove.com/decimal/telco.html}},
using a pure Python decimal floating point implementation. The results we see in
these two benchmarks seem to repeat themselves in other benchmarks using
object-oriented code, for purely numerical algorithms the speedups are a lot
lower.

The benchmarks were run on an otherwise idle Intel Core2 Duo P8400 processor
with 2.26 GHz and 3072 KB of cache on a machine with 3GB RAM running Linux
2.6.35. We compared the performance of various Python implementations on the
benchmarks. As a baseline, we used the standard Python implementation in C,
CPython 2.6.6\footnote{\texttt{http://python.org}}, which uses a bytecode-based
interpreter. We compare it against four versions of PyPy's Python interpreter,
all of them with JIT enabled. The PyPy baseline does not enable maps or type
versions. Then we have a version each where maps and versions are enabled alone
and finally a version with both.

@@

Versioned types speed up both benchmarks by a significant factor of around 7.
The speed advantage of maps alones is a lot less clear. Maps also have a memory
advantage which we did not measure here. By themselves, maps improved the
Richards benchmark slightly, but made the Telco benchmark slower. Enabling both
maps and versioned types together yields a significant improvement over just
versioned types for Richards. XXX good explanation. For Telco, enabling both
does not change much.

>>>>

For space reasons we cannot perform a full evaluation here, but still want to
present some benchmark numbers. We chose to present two benchmarks, a port of
the classical Richards benchmark in Python and a Python version of the Telco
decimal benchmark\footnote{\texttt{http://speleotrove.com/decimal/telco.html}},
using a pure Python decimal floating point implementation. The results we see in
these two benchmarks seem to repeat themselves in other benchmarks using
object-oriented code; for purely numerical algorithms the speedups are 
significantly smaller.

The benchmarks were run on an otherwise idle Intel Core2 Duo P8400 processor
with 2.26 GHz and 3072 KB of cache on a machine with 3GB RAM running Linux
2.6.35. We compared the performance of various Python implementations on the
benchmarks. As a baseline, we used the standard Python implementation in C,
CPython 2.6.6\footnote{\texttt{http://python.org}}, which uses a bytecode-based
interpreter. We compare it against four versions of PyPy's Python interpreter,
all of them with JIT enabled. The PyPy baseline does not enable maps or type
versions. We then benchmarked PyPy, first using each technique separately,
and finally using both together.

@@

Versioned types speed up both benchmarks by a significant factor of around 7.
The speed advantage of maps alone is a lot less clear. Maps also have a memory
advantage which we did not measure here. By themselves, maps improved the
Richards benchmark slightly, but made the Telco benchmark slower. Enabling both
maps and versioned types together yields a significant improvement over just
versioned types for Richards. XXX good explanation. For Telco, enabling both
has little effect over the gains for versioned types alone.
